% % include the figures path relative to the master file
% \graphicspath{ {./content/results/figures/} }

\section{Experiments and Validation }

\subsection{Datasets}

In this work, we validated our classification framework using two different datasets.

\begin{description}

\item[SERI]- datasets were acquired by Singapore Eye Research Institute (SERI), using CIRRUS TM (Carl Zeiss Meditec, Inc., Dublin, CA) \ac{sdoct} device. The datasets consist of 32 \ac{oct} volumes (16 \ac{dme} and 16 normal cases). Each volume contains 128 B-sane with  dimension of 512 $\times$ 1024 pixels.  All \ac{sdoct} images are read and assessed by trained graders and identifies as normal or \ac{dme} cases based on evaluation of retinal thickening, hard exudates, intraretinal cystoid space formation and subretinal fluid.

\item[Duke] - datasets published by Srinivasan et al. \cite{Srinivasan2014} were acquired in Institutional Review Board-approved protocols using Spectralis \ac{sdoct} (Heidelberg Engineering Inc., Heidelberg, Germany) imaging at Duke University, Harvard University and the University of Michigan. This datasets consist of 45 \ac{oct} volumes (15 \ac{amd}, 15 \ac{dme} and 15 normal). In this study we only consider a subset of the original data containing 15 \ac{dme} and 15 normal \ac{oct} volumes.

\end{description}

\subsection{Experiments \& results}

Both datasets are filtered to attenuate the effect of speckle noise. 
SIRE dataset is processed using \ac{nlm} as stated in Sect.\,\ref{subsec:prepro}.
The different parameters were empirically tested and fixed such that the patch size, the search window and the filtering parameter were set to $(15 \times 15)$, $(35 \times 35)$ and $0.4$, respectively.
However, Duke dataset is already filtered using BM3D method~\cite{Srinivasan2014}.
For both datasets, \ac{lbp} and \ac{lbptop} features are extracted for different sampling points of 8, 16 and 24 for radius of 1, 2 and 3, respectively.
Two different mapping strategies are used: (i) the 2D B-scan for \ac{lbp} or the 3D volume for \ac{lbptop} and (ii) a set of 2D \ac{sw} of size $(7 \times 7)$ for \ac{lbp} or the 3D sub-volume for \ac{lbptop} of size $(7 \times 7 \times 7)$.
For the high-level representation, when \ac{pca} is applied, the eigenvectors associated with the largest $99\%$ cumulative eigenvalues are selected to reduce the number of dimensions. In \ac{bow} approach, an empirical search was performed to find the optimal number of visual words which is finally fixed to 32. 
The number of trees for each \ac{rf} classifier was fixed to 100.
For evaluation purposes, the results are cross-validated using a \ac{lopo} strategy. Thus, at each round a pair $(\ac{dme}, normal)$ is selected for testing while the rest acts as trainig.
Performing \ac{lopo} cross validation, has the limitation that despite acheaving robust results due to the cross validation, no variance can be reported.
However, and despite this limitation, \ac{lopo} has been choosed due to the reduced amount of \ac{oct} volumes available.

\begin{description}

\item[Experiment \#1] is carried out on SERI dataset. Both low and high level feature representation are extracted and tested. The results are reported in Table~\ref{tab:SERI-data}.

\item[Experiment \#2] is carried out on the Duke dataset~\cite{Srinivasan2014}. The \ac{oct} volumes provided by this dataset are cropped, with different sizes. 
Subsequently, the experiments involving the mapping using 2D B-scan do not comply with these requirements and thus are not carried out.
The obtained results for this experiment are shown in Table~\ref{tab:Duke-data}.

\item[Experiment \#3] presents a comparison of our best approaches with the method reported in~\cite{Venhuizen2015} in-house implemented and are expressed in Table~\ref{tab:ComparisonRefandOurs}.

\end{description}
% The SERI datasets are provided in complete \ac{oct} volumes by 512$\times$1024$\times$128 dimensions. Using this datasets, first the three low-level features such as \ac{lbp}, \ac{lbp}+\ac{pca} and \ac{lbptop} are extracted. The rotation invariant uniform ($riu2$) descriptors are calculated with the $P$ number of 8, 16 and 24 for the radius if 1, 2 and 3 respectively. The features are classified using RF with 100 tress. Table \ref{tab:LbPTopVolumeResult} shows the relative results for $8riu2$, $16riu2$, $24riu2$ and their combination $8riu2 + 16riu2 + 24riu2$. The results are presented in terms of \ac{se} and \ac{sp} percentages.  

% The second experiment is carried out using high-level features and \ac{bow} approach, on SERI datasets. The first high-level feature \ac{lbp}+\ac{bow} is obtained by applying \ac{bow} with 32 visual-words on the previously low-level \ac{lbp} features (applied on each B-scan). The second and third high-level descriptors are obtained using a dense approach by applying the \ac{sw} of size (7$\times$7) on each B-scan and \ac{sw} of size (7$\times$7$\times$7) to the whole volume respectively. \ac{lbp}+\ac{bow}+\ac{sw} represent the second high-level feature where the 2D-\ac{lbp} features are extracted for each sliding window on each B-scan and the visual-words are selected from the pool, consisting of their histograms. The third high-level feature, \ac{lbptop}+\ac{bow}+\ac{sw}, is defined using \ac{lbptop}. By using the sliding window the 3D-\ac{lbp} features are extracted for each patch. Same as previous experiment with low-level features, the descriptors are calculated with the $P$ number of 8, 16 and 24 for the radius if 1, 2 and 3 respectively. The obtained results of this experiment are illustrated in Tab. \ref{tab:SERIBoWResult}. 

% In order to compare our proposed framework the third experiment is carried out using the subsection of Duke datasets \cite{Srinivasan2014}. The OCT volumes provided by this datasets are of different volume size, cropped and denoised by the method of authors choice. Subsequently only the second experiment with high-level features and low-level \ac{lbptop} features comply with these requirements. The number of visual-words and the size of \ac{sw} for 2D and 3D features are the same than the previous experiment. The 2D and 3D \ac{lbp} features are extracted with $P$ number of 8, 16 and 24 for the radius if 1, 2 and 3 respectively. The obtained results for this experiment are shown in Tab. \ref{tab:DukeBoWResult}.
%----------

%%% Local Variables: 
%%% mode: latex
%%% TeX-master: "../../master"
%%% End: 
