\documentclass{llncs}

%% Latex documents that need direct input
\input{latex/filesystem/package.tex}        % contains the latex packages
\input{content/frontmatter.tex}             % contains the Title and Autor info
\input{latex/filesystem/fileSetup.tex}      % contains package and variables init.
\input{content/acronym_definition.tex}      % contains the acronims 

%% Select inputing only one part of the document
%\includeonly{content/intro/intro}   % the file wihtout .tex
%\includeonly{content/other/other_content}
 
\begin{document} 
\maketitle 

\begin{abstract}
\acresetall  % reset the acronyms from the title (if any)
  Breast cancer is the second most common cancer and the leading cause of cancer death among women.
  Medical imaging has become an indispensable tool for its diagnosis and follow up.
  During the last decade, the medical community has promoted to incorporate \ac{us} screening as part of the standard routine.
  The main reason for using \ac{us} imaging is its capability to differentiate benign from malignant masses, when compared to other imaging techniques.
  The increasing usage of \ac{us} imaging encourages the development of \ac{cad} systems applied to \ac{bus} images.  
  However accurate delineations of the lesions and structures of the breast are essential for \ac{cad} systems in order to extract information needed to perform diagnosis.

  This article proposes a highly modular and flexible framework for segmenting lesions and tissues present in \ac{bus} images.
  The proposal takes advantage of optimization strategies using super-pixels and high-level descriptors, which are analogous to the visual cues used by radiologists.
  Qualitative and quantitative results are provided stating a performance within the range of the state-of-the-art.
\end{abstract}

\keywords{Breast Ultra-Sound, BI-RADS lexicon, Optimization based Segmentation, Machine-Learning based Segmentation, Graph-Cuts}

%% Incldue the content without .tex extension
\acresetall  % reset the acronyms from the abstract
\include*{content/intro/intro}          % the file wihtout .tex
\include*{content/method/method}        
%\include*{content/features/features}    
\include*{content/results/results}

\section{Conclusions}
This work presents a segmentation strategy to delineate lesions in \ac{bus} images using an optimization framework that takes advantage of all the facilities available when using \ac{ml} techniques.
Despite the limitation that the final segmentation is subject to the super-pixels' boundaries, the \ac{aov} results here reported are similar to those reported by other methodologies in the literature.
A higher \ac{aov} result can be achieved by deforming the delineation resulting from the proposed framework using this to initialize a second post-processing step based on \ac{acm}. In this manner the contour constrains could be applied to achieve a more natural delineation.

%\acknowledgments     %>>>> equivalent to \section*{ACKNOWLEDGMENTS}       
% 
%This unnumbered section is used to identify those who have aided the authors in understanding or accomplishing the work presented and to acknowledge sources of funding.  

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%% References %%%%%


\bibliography{./content/literature_review}   %>>>> bibliography data in report.bib
\bibliographystyle{spiebib}   %>>>> makes bibtex use spiebib.bst

\end{document} 
